% Jamal - ATS-friendly LaTeX resume (single-page)
\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage[colorlinks=true,linkcolor=black,urlcolor=black]{hyperref}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{array}
\usepackage{fontawesome5}
\setlength{\parskip}{4pt}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0pt}{}
\titlespacing*{\section}{0pt}{8pt}{4pt}

% Header
\begin{document}
\begin{center}
  {\LARGE \textbf{Jamal}}\\[2pt]
  \faAt\ \href{mailto:jamaludheen779@gmail.com}{jamaludheen779@gmail.com}
  \ | \ \faPhone\ +91 98846 99435
  \ | \ \faGithub\ \href{https://github.com/Jamaludheen2426}{github.com/Jamaludheen2426}
  \ | \ \faLinkedin\ \href{https://www.linkedin.com/in/jamal2426/}{linkedin.com/in/jamal2426/}
\end{center}

\section*{Summary}
Full-stack developer with experience in .NET and React. Built scalable web apps, real-time features, and RESTful APIs. Strong in database design and clean architecture.

\section*{Skills}
\textbf{Languages:} C\#, JavaScript, Java, HTML/CSS\\
\textbf{Frameworks:} .NET Framework, .NET Core, ASP.NET, ASP.NET Core, React.js, Next.js\\
\textbf{Databases/ORM:} MySQL, MongoDB, Entity Framework, LINQ\\
\textbf{Web:} RESTful APIs, Web API, MVC\\
\textbf{Tools:} Git/GitHub, Visual Studio, VS Code, Postman, Swagger\\

\section*{Experience}
\textbf{FullStack Developer} \hfill Jul 2024 -- Present\\
MAKINUS\\
\begin{itemize}[leftmargin=*,nosep]
  \item Developed enterprise apps using .NET Core and ASP.NET for network installation automation and engineering processes.
  \item Implemented data visualization and backend services for real-time telemetry processing.
  \item Contributed to scalable architecture and database design with Entity Framework and MySQL.
\end{itemize}

\textbf{Java Developer Intern} \hfill Apr 2023\\
ICONIX SOFTWARE SOLUTION\\
\begin{itemize}[leftmargin=*,nosep]
  \item Worked on backend development focusing on database integration and API development.
  \item Practiced OOP, SDLC, and enterprise best practices.
\end{itemize}

\section*{Projects}
\textbf{College MERN Chat App} \hfill Team Project\\
\emph{MongoDB, Express, React, Node.js, Socket.IO, Postman, Swagger}\\
Real-time messaging with authentication and message persistence; responsive UI and RESTful APIs.\\

\textbf{CRUD Generator (Practice)}\\
\emph{Next.js, React, Vercel}\\
Demonstration CRUD generator available on GitHub and deployed on Vercel.

\section*{Education}
\textbf{B.Sc. in Computer Science} \hfill 2021 -- 2024\\
Sadakathulla Appa College, Tirunelveli \hfill CGPA: 7.9/10.0 (Grade A+)

\end{document}
